Plot responses to model covariates to inform threshold choices for VOCC

### 2019-08-29 analysis/VOCC/1-biomass-temp-models-fixed.Rmd
various minor housekeeping

Species
```{r}
species <- params$species
# # Species run so far...
# species <- "Arrowtooth Flounder"
# species <- "Pacific Cod"
# species <- "Sablefish"
# species <- "Silvergray Rockfish"
 species <- "Lingcod"
# species <- "North Pacific Spiny Dogfish" # note: using all data for maturity thresholds

@@

Region 
```{r}
 region <- "All synoptic surveys"
# region <- "Both odd year surveys"
# region <- "West Coast Vancouver Island"
# region <- "West Coast Haida Gwaii"
```

@@

  data <- do_data %>% mutate(depth = raw_depth) %>% # filter(year != 2016) %>% 
    filter(ssid %in% model_ssid) %>% 
    filter(!is.na(raw_depth)) %>% filter(!is.na(temp)) %>%
    select(X, Y, X10, Y10, adult_density, imm_density, depth_scaled, depth_scaled2, temp_scaled, temp_scaled2, depth_mean, depth_sd, temp_mean, temp_sd, trawled, any_rock, muddy, sandy, year, ssid, fishing_event_id, depth, temp)  
```

>>>>

Species
```{r}
species <- params$species
# # Species run so far...
# species <- "Arrowtooth Flounder"
# species <- "Pacific Cod"
# species <- "Sablefish"
# species <- "Silvergray Rockfish"
# species <- "Lingcod"
# species <- "North Pacific Spiny Dogfish" # note: using all data for maturity thresholds

@@

Region 
```{r}
# region <- "All synoptic surveys"
 region <- "Both odd year surveys"
 region <- "West Coast Vancouver Island"
 region <- "West Coast Haida Gwaii"
```

@@

  data <- do_data %>% mutate(depth = raw_depth) %>% # filter(year != 2016) %>% 
    filter(ssid %in% model_ssid) %>% 
    filter(!is.na(raw_depth)) %>% filter(!is.na(temp)) #%>% select(X, Y, X10, Y10, adult_density, imm_density, depth_scaled, depth_scaled2, temp_scaled, temp_scaled2, depth_mean, depth_sd, temp_mean, temp_sd, trawled, any_rock, muddy, sandy, year, ssid, fishing_event_id, depth, temp)  
```

### 2019-08-29 analysis/VOCC/2-biomass-trends.Rmd
various minor housekeeping

  adult_predictions$est_exp <- exp(adult_predictions$est) * 10000
  imm_predictions$est_exp <- exp(imm_predictions$est) * 10000

>>>>

  # to convert from kg/m2 to kg/hectare multiply by 10000
  adult_predictions$est_exp <- exp(adult_predictions$est) * 10000
  imm_predictions$est_exp <- exp(imm_predictions$est) * 10000

### 2019-08-29 analysis/VOCC/3-variable-response-plots.Rmd
various minor housekeeping

Species
```{r}
# species <- params$species
# # Species run so far...
# species <- "Arrowtooth Flounder"
# species <- "Pacific Cod"
# species <- "Sablefish"
# species <- "Silvergray Rockfish"
 species <- "Lingcod"
# species <- "North Pacific Spiny Dogfish" # note: using all data for maturity thresholds

@@

date <- Sys.time()

>>>>

Species
```{r}
# species <- params$species
# # Species run so far...
# species <- "Arrowtooth Flounder"
# species <- "Pacific Cod"
# species <- "Sablefish"
# species <- "Silvergray Rockfish"
# species <- "Lingcod"
# species <- "North Pacific Spiny Dogfish" # note: using all data for maturity thresholds

@@

date <- Sys.Date()
